\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
heading changes
fig 5's axis cropped and intro to sec 7 reorganized

\subsection{Agent Behavior}

@@

\section{CONFIGURABILITY}
\label{sec:config}

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects agent performance \commentd{performance is a vague term, but I
don't want to talk about dependent vars just yet}, three policies are evaluated: stop sign,
traffic signal, and autonomous reservation. These are compared with all other
parameters fixed:

\begin{enumerate}
  \item the map (a 6 by 7 mile slice of downtown Austin, Texas
        \footnote{bounded by the Mopac and Springdale Road horizontally,
        and Oltorf Street and Koenig Lane vertically})
  \item dt = 0.1 seconds
  \item the agents spawned and their routes -- a continuous generator creates
        one new agent every 1 simulation second, with a uniformly random
        starting position and goal
  \item the duration of the experiment: one hour
\end{enumerate}

Each experiment is deterministically reproducible. A seed for the pseudo-random
number generator, the input graph, and the generators' configuration fully
determine the outcome of any simulation \footnote{This determinism may break
  down when generators use worker threads, since routes may be computed in
different orders, causing agents to enter the road at different times.}. After
setting up a scenario in the UI, users can save this configuration for
resimulation.

>>>>

@@

\section{EXTENDING AORTA}
\label{sec:config}

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects agent performance \commentd{performance is a vague term, but I
don't want to talk about dependent vars just yet}, three policies are evaluated: stop sign,
traffic signal, and autonomous reservation.

\subsection{Experimental Setup}

The experiment simulates a 6 by 7 mile slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, for one hour. The step duration is fixed at
0.1 seconds. While the intersection policies vary, the agents spawned and their
routes remain the same. A generator creates one new agent every 1 simulation
second, with a uniformly random starting position and goal.

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
  determinism may break down when generators use worker threads, since routes
  may be computed in different orders, causing agents to enter the road at
different times.}. After setting up a scenario in the UI, users can save this
configuration for resimulation.
